Computer Science House Constitution

### 2022-02-13 constitution.tex
constitution: add a process for waiving candidacy requirements

\asubsection{Overriding Directorships Qualifications}
Qualifications pertaining to a specific directorship election can be overriding via a Constitutional Override, as explained in \ref{Semantic Changes}. Overrides will apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.

>>>>

\asubsection{Waiving of Requirements}
\begin{enumerate}
  \item The following requirements may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must have at least one full semester of House membership as an Active Member
      \item Candidates must reside on floor during the term of office
    \end{enumerate}
  \item This process waives the enumerated requirements for a given election for all candidates on a per-directorship basis
\end{enumerate}
